String Constraints with Regex-Counting and String-Length Solved Efficiently

### 2023-05-04 2023-1-19/figures/cactus_plot_stackoverflow.tex

\documentclass[11pt]{standalone}
\usepackage{color}
\usepackage{tikz}
\usepackage{pgfplots}
\usepgfplotslibrary{fillbetween}
\pgfplotsset{compat=1.16}
\begin{document}
\definecolor{colourCVC5}{HTML}{25333D}
\definecolor{colourOstrichCEA}{HTML}{0065AB}
\definecolor{colourOstrich}{HTML}{8939AD}
\definecolor{colourZ3str3}{HTML}{007E7A}
\definecolor{colourZ3seq}{HTML}{CD3517}
\definecolor{colourZ3str3RE}{HTML}{318700}
\definecolor{colourZ3-Trau}{HTML}{80746D}
\resizebox{.95\textwidth}{!}{\pgfplotsset{scaled x ticks=false}\pgfplotsset{scaled y ticks=false}\begin{tikzpicture}\begin{axis}[title=stackoverflow,xlabel=Solved instances,ylabel=Time (s),,legend columns=2,legend style={nodes={scale=0.5, transform shape}, fill=none,anchor=east,align=center },axis line style={draw=none}, xtick pos=left, ytick pos=left, ymajorgrids=true, legend style={draw=none},x post scale=2,y post scale=1]
\addplot[name path=pathCVC5 , colourCVC5, line width=1.5pt] coordinates {(1,0.004)(167.5,0.7233143712574851)(501.5,2.424832335329341)(835.5,4.471230538922155)(1169.5,7.107095808383233)(1503.5,10.389062874251497)(1837.5,14.099278443113771)(2171.5,18.174152694610775)(2505.5,22.56328143712575)(2839.5,27.240485029940118)(3173.5,32.199152694610774)(3507.5,37.44004491017964)(3841.5,42.9565)(4175.5,48.74484730538922)(4509.5,54.80647305389222)(4843.5,61.164)(5177.5,67.82197005988024)(5511.5,74.77786826347305)(5845.5,82.05068862275449)(6179.5,89.64715269461078)(6513.5,97.57394011976048)(6847.5,105.86460479041916)(7181.5,114.52601796407185)(7515.5,123.56620359281438)(7849.5,133.02156886227544)(8183.5,142.95500898203593)(8517.5,153.42188023952096)(8851.5,164.45122754491018)(9185.5,176.06351796407185)(9519.5,188.34054790419162)(9853.5,201.33261676646708)(10187.5,215.11561676646707)(10521.5,229.66456886227544)(10855.5,244.98857185628742)(11189.5,261.1554341317365)(11523.5,278.16943113772453)(11857.5,296.0684610778443)(12191.5,314.8944161676647)(12525.5,334.76406886227545)(12859.5,355.686380239521)(13193.5,377.6354700598802)(13527.5,400.7926766467066)(13861.5,425.26753293413174)(14195.5,451.1214670658683)(14529.5,478.60874251497006)(14863.5,507.8448353293413)(15197.5,538.9790179640718)(15531.5,572.0008802395209)(15865.5,607.0877035928144)(16199.5,644.1859670658683)(16533.5,683.3988143712575)(16867.5,724.9113922155688)(17201.5,768.7641467065869)(17535.5,815.1436047904191)(17869.5,864.0901227544911)(18203.5,915.7329730538922)(18537.5,970.133739520958)(18871.5,1027.413368263473)(19205.5,1088.0779311377246)(19539.5,1152.6376377245508)(19873.5,1221.4731976047904)(20207.5,1294.8711916167663)(20541.5,1373.1157784431136)(20875.5,1457.0711646706588)(21209.5,1547.5486616766466)(21543.5,1645.0836676646707)(21877.5,1749.5506556886228)(22211.5,1861.3744251497005)(22545.5,1980.2774341317365)(22879.5,2106.45052994012)(23213.5,2240.55351497006)(23547.5,2382.9252964071857)(23881.5,2533.9247964071856)(24215.5,2694.0401377245507)(24549.5,2863.199398203593)(24883.5,3042.0251796407188)(25217.5,3230.280344311377)(25551.5,3428.0554790419164)(25885.5,3636.7262814371256)(26219.5,3857.1243083832333)(26553.5,4090.237161676647)(26887.5,4338.172107784431)(27221.5,4602.643706586827)(27555.5,4887.577766467066)(27889.5,5196.619589820359)(28223.5,5533.495835329341)(28557.5,5904.957110778443)(28891.5,6318.40652994012)(29225.5,6784.988535928144)(29559.5,7319.875413173652)(29893.5,7949.884458083832)(30227.5,8725.226431137724)(30561.5,9789.064071856288)(30895.5,11265.184853293413)(31229.5,13413.724155688624)(31563.5,16944.67256287425)(31897.5,22938.68886227545)(32231.5,32316.48101497006)(32549.5,45359.79038741722)(32702,53261.719)};
\addlegendentry{CVC5}

\addplot[name path=pathOstrichCEA , colourOstrichCEA, line width=1.5pt] coordinates {(1,1.069)(190.5,232.6589)(570.5,709.6480842105263)(950.5,1196.6337184210527)(1330.5,1690.1221210526317)(1710.5,2189.6400842105263)(2090.5,2694.497357894737)(2470.5,3204.0573736842107)(2850.5,3718.6741578947367)(3230.5,4238.482794736841)(3610.5,4764.7214894736835)(3990.5,5298.296757894736)(4370.5,5841.281960526316)(4750.5,6395.202660526315)(5130.5,6961.350839473685)(5510.5,7540.993026315789)(5890.5,8133.372015789473)(6270.5,8734.822897368422)(6650.5,9342.967752631579)(7030.5,9956.752307894736)(7410.5,10575.234568421052)(7790.5,11198.100728947367)(8170.5,11824.840531578946)(8550.5,12455.626292105264)(8930.5,13090.247586842104)(9310.5,13728.575228947368)(9690.5,14370.440260526317)(10070.5,15015.841252631579)(10450.5,15664.630397368423)(10830.5,16317.030813157895)(11210.5,16973.154363157893)(11590.5,17632.737636842106)(11970.5,18295.751634210526)(12350.5,18962.31434736842)(12730.5,19632.349584210526)(13110.5,20305.699439473687)(13490.5,20982.394255263156)(13870.5,21662.506336842103)(14250.5,22345.894881578948)(14630.5,23032.483915789475)(15010.5,23722.286118421052)(15390.5,24415.212605263157)(15770.5,25111.176465789475)(16150.5,25810.02410263158)(16530.5,26511.73647105263)(16910.5,27216.409768421054)(17290.5,27924.022686842105)(17670.5,28634.736831578946)(18050.5,29348.564321052632)(18430.5,30065.47053947368)(18810.5,30785.48525)(19190.5,31508.688036842104)(19570.5,32235.248236842108)(19950.5,32965.0526631579)(20330.5,33698.28517105264)(20710.5,34434.81481052632)(21090.5,35174.532952631576)(21470.5,35917.895857894735)(21850.5,36665.28371052632)(22230.5,37416.66357368421)(22610.5,38172.28100789474)(22990.5,38931.92542368421)(23370.5,39695.625260526314)(23750.5,40463.389355263156)(24130.5,41235.613436842104)(24510.5,42012.476486842104)(24890.5,42793.96287368421)(25270.5,43580.56005526315)(25650.5,44372.39037105263)(26030.5,45169.62203947368)(26410.5,45972.09492631579)(26790.5,46780.44576842106)(27170.5,47595.067805263156)(27550.5,48416.389299999995)(27930.5,49244.825065789475)(28310.5,50080.321313157896)(28690.5,50923.3093368421)(29070.5,51774.13953684211)(29450.5,52633.453644736845)(29830.5,53501.829744736846)(30210.5,54379.64974210526)(30590.5,55267.43845263158)(30970.5,56166.53594210526)(31350.5,57077.05190263158)(31730.5,57999.50882631579)(32110.5,58934.752134210525)(32490.5,59885.838323684206)(32870.5,60853.76433421053)(33250.5,61840.456797368424)(33630.5,62847.4605)(34010.5,63880.007623684214)(34390.5,64943.45741578947)(34770.5,66040.62170789474)(35150.5,67180.7566394737)(35530.5,68371.20348421052)(35910.5,69634.29873421052)(36290.5,71007.77509473685)(36670.5,72553.45386842104)(37050.5,74590.8398131579)(37260.5,77017.990675)(37282,77894.058)};
\addlegendentry{OstrichCEA}

\addplot[name path=pathOstrich , colourOstrich, line width=1.5pt] coordinates {(1,0.973)(183,190.30856164383562)(548,594.3603315068493)(913,1024.961002739726)(1278,1469.2798904109588)(1643,1923.6285232876712)(2008,2386.440526027397)(2373,2857.0123945205482)(2738,3335.2412931506847)(3103,3820.518504109589)(3468,4312.556301369863)(3833,4811.463101369864)(4198,5316.991939726027)(4563,5828.562306849315)(4928,6346.063736986301)(5293,6868.94305479452)(5658,7396.841920547946)(6023,7929.662317808219)(6388,8467.604142465754)(6753,9010.742153424659)(7118,9558.934805479452)(7483,10111.938605479452)(7848,10669.474978082191)(8213,11231.314112328768)(8578,11797.621369863013)(8943,12368.65250410959)(9308,12944.311830136987)(9673,13524.519564383561)(10038,14109.451419178082)(10403,14698.853712328768)(10768,15293.112660273973)(11133,15892.433191780823)(11498,16496.828142465754)(11863,17106.316189041096)(12228,17721.04000547945)(12593,18340.346950684932)(12958,18964.554947945202)(13323,19594.05018082192)(13688,20228.820687671232)(14053,20869.080038356162)(14418,21514.670046575342)(14783,22165.900589041095)(15148,22822.877701369864)(15513,23485.61907123288)(15878,24154.566920547943)(16243,24829.88501369863)(16608,25511.430641095892)(16973,26198.8236630137)(17338,26892.730293150686)(17703,27593.722350684933)(18068,28301.48203561644)(18433,29016.173605479453)(18798,29737.934356164384)(19163,30466.729484931508)(19528,31202.92680821918)(19893,31946.9248630137)(20258,32698.838134246576)(20623,33459.216728767125)(20988,34229.22386849315)(21353,35008.99332054795)(21718,35798.51410410959)(22083,36598.632827397254)(22448,37409.98307945205)(22813,38232.88135342466)(23178,39067.59715616438)(23543,39915.206906849315)(23908,40775.91306849315)(24273,41650.684063013694)(24638,42540.330361643835)(25003,43445.31521643835)(25368,44367.7068)(25733,45309.33676438356)(26098,46271.140583561646)(26463,47254.96390684932)(26828,48263.57510136987)(27193,49300.231649315065)(27558,50368.124427397255)(27923,51470.418468493146)(28288,52611.19690136986)(28653,53795.38869041095)(29018,55029.08482465754)(29383,56320.12154520548)(29748,57678.96482465754)(30113,59114.90866575342)(30478,60647.17013150685)(30843,62287.70946575342)(31208,64046.39155890411)(31573,65948.76017808219)(31938,68015.45561917809)(32303,70268.4742739726)(32668,72725.02970136987)(33033,75449.96638630137)(33398,78510.05700821918)(33763,81999.3380219178)(34128,86050.69222191781)(34493,90831.67789315069)(34858,96740.15275342466)(35223,104550.05547123287)(35588,116337.4376410959)(35779,125163.37964705883)(35789,125692.196)};
\addlegendentry{Ostrich}

\addplot[name path=pathZ3str3 , colourZ3str3, line width=1.5pt] coordinates {(1,0.012)(146,1.978233676975945)(437,6.271)(728,10.63781443298969)(1019,15.179)(1310,19.835)(1601,24.491)(1892,29.147)(2183,33.827536082474225)(2474,38.724)(2765,43.671)(3056,48.636051546391755)(3347,53.813)(3638,59.053546391752576)(3929,64.473)(4220,70.01970103092785)(4511,75.778)(4802,81.598)(5093,87.44253608247422)(5384,93.503)(5675,99.614)(5966,105.74201030927836)(6257,112.081)(6548,118.483)(6839,124.9422268041237)(7130,131.615)(7421,138.308)(7712,145.08378350515463)(8003,152.059)(8294,159.043)(8585,166.03229209621992)(8876,173.212)(9167,180.487)(9458,187.762)(9749,195.08520618556702)(10040,202.625)(10331,210.191)(10622,217.77952577319587)(10913,225.583)(11204,233.44001030927836)(11495,241.445)(11786,249.593)(12077,257.8093848797251)(12368,266.234)(12659,274.69963230240546)(12950,283.382)(13241,292.1369484536083)(13532,301.108)(13823,310.1481237113402)(14114,319.401)(14405,328.73513402061855)(14696,338.284)(14987,347.95956013745706)(15278,357.8412268041237)(15569,367.892)(15860,378.1011271477663)(16151,388.526)(16442,399.09973539518904)(16733,409.8684982817869)(17024,420.836)(17315,431.97982817869416)(17606,443.3423608247423)(17897,454.9270206185567)(18188,466.716)(18479,478.7367113402062)(18770,491.00674570446733)(19061,503.5473642611684)(19352,516.3713711340206)(19643,529.517793814433)(19934,543.0013092783505)(20225,556.8603848797251)(20516,571.1063608247422)(20807,585.7789175257732)(21098,600.9315738831615)(21389,616.5986323024056)(21680,632.778206185567)(21971,649.4465979381444)(22262,666.6643917525772)(22553,684.4916597938144)(22844,702.9503024054983)(23135,722.1009312714777)(23426,742.000879725086)(23717,762.6884123711341)(24008,784.2621340206185)(24299,806.8419381443299)(24590,830.5944329896906)(24881,855.6907972508591)(25172,882.2354776632303)(25463,910.5732749140893)(25754,940.9522302405497)(26045,973.7337250859107)(26336,1009.525501718213)(26627,1049.177388316151)(26918,1094.1484364261169)(27209,1146.7408178694157)(27500,1210.8287972508592)(27791,1295.0530343642613)(28082,1428.52512371134)(28373,1936.0622164948454)(28541,3951.5852444444445)(28565,4945.078)};
\addlegendentry{Z3str3}

\addplot[name path=pathZ3seq , colourZ3seq, line width=1.5pt] coordinates {(1,0.011)(181.5,2.298024861878453)(543.5,7.39196132596685)(905.5,12.846621546961325)(1267.5,18.578)(1629.5,24.44856629834254)(1991.5,30.594629834254146)(2353.5,37.014)(2715.5,43.66661602209945)(3077.5,50.57362154696132)(3439.5,57.753)(3801.5,65.08817403314917)(4163.5,72.6765)(4525.5,80.4550276243094)(4887.5,88.4337955801105)(5249.5,96.6675)(5611.5,105.07338950276242)(5973.5,113.75666574585635)(6335.5,122.7165)(6697.5,131.92012154696133)(7059.5,141.41022651933702)(7421.5,151.196044198895)(7783.5,161.28051104972374)(8145.5,171.66944198895027)(8507.5,182.3868591160221)(8869.5,193.474908839779)(9231.5,204.9389502762431)(9593.5,216.7948950276243)(9955.5,229.06955801104974)(10317.5,241.797091160221)(10679.5,255.0154502762431)(11041.5,268.74189226519337)(11403.5,283.05802486187844)(11765.5,297.9990718232044)(12127.5,313.6326961325967)(12489.5,330.0478287292818)(12851.5,347.36489779005524)(13213.5,365.62986464088397)(13575.5,385.0328149171271)(13937.5,405.66013259668506)(14299.5,427.5818314917127)(14661.5,450.83144475138124)(15023.5,475.5672955801105)(15385.5,502.0523453038674)(15747.5,530.0259751381216)(16109.5,559.3107375690607)(16471.5,589.8519640883978)(16833.5,621.6678066298342)(17195.5,654.8743176795581)(17557.5,689.4013121546961)(17919.5,725.3846961325967)(18281.5,762.8980635359117)(18643.5,801.907591160221)(19005.5,842.5096629834254)(19367.5,884.8020718232044)(19729.5,928.861544198895)(20091.5,974.7612099447514)(20453.5,1022.6342651933702)(20815.5,1072.5725607734807)(21177.5,1124.8395055248618)(21539.5,1179.584991712707)(21901.5,1237.1880303867404)(22263.5,1297.957046961326)(22625.5,1362.265491712707)(22987.5,1430.3952762430938)(23349.5,1502.6981519337016)(23711.5,1579.696502762431)(24073.5,1661.6038812154698)(24435.5,1748.4525828729281)(24797.5,1840.9641022099447)(25159.5,1938.9034005524863)(25521.5,2042.6551602209943)(25883.5,2153.1485220994473)(26245.5,2271.2495)(26607.5,2396.9298314917123)(26969.5,2530.6465359116023)(27331.5,2672.95844198895)(27693.5,2824.6903425414366)(28055.5,2986.2353867403317)(28417.5,3158.2669364640883)(28779.5,3341.9625939226516)(29141.5,3538.530229281768)(29503.5,3748.9704861878454)(29865.5,3973.6326353591157)(30227.5,4215.252831491713)(30589.5,4476.184969613259)(30951.5,4760.791403314917)(31313.5,5071.179861878453)(31675.5,5412.076848066298)(32037.5,5786.981693370165)(32399.5,6205.653919889503)(32761.5,6683.778737569061)(33123.5,7242.432157458564)(33485.5,7909.979223756905)(33847.5,8733.536740331492)(34209.5,9802.194723756906)(34571.5,11351.004914364641)(34933.5,13998.519212707182)(35279.5,19650.679766666664)(35446,25499.5)};
\addlegendentry{Z3seq}

>>>>

\documentclass[11pt]{standalone}
\usepackage{color}
\usepackage{tikz}
\usepackage{pgfplots}
\usepgfplotslibrary{fillbetween}
\pgfplotsset{compat=1.16}
\begin{document}
\definecolor{colourCVC5}{HTML}{25333D}
\definecolor{colourOstrichCEA}{HTML}{0065AB}
\definecolor{colourOstrich}{HTML}{8939AD}
\definecolor{colourZ3str3}{HTML}{007E7A}
\definecolor{colourZ3seq}{HTML}{CD3517}
\definecolor{colourZ3str3RE}{HTML}{318700}
\definecolor{colourZ3-Trau}{HTML}{80746D}
\resizebox{.95\textwidth}{!}{\pgfplotsset{scaled x ticks=false}\pgfplotsset{scaled y ticks=false}\begin{tikzpicture}\begin{axis}[title=stackoverflow,xlabel=Solved instances,ylabel=Time (s),,legend columns=2,legend style={nodes={scale=0.5, transform shape}, fill=none,anchor=east,align=center },axis line style={draw=none}, xtick pos=left, ytick pos=left, ymajorgrids=true, legend style={draw=none},x post scale=2,y post scale=1]
\addplot[name path=pathCVC5 , colourCVC5, line width=1.5pt, dashed, dash pattern=on 2pt off 8pt] coordinates {(1,0.004)(167.5,0.7233143712574851)(501.5,2.424832335329341)(835.5,4.471230538922155)(1169.5,7.107095808383233)(1503.5,10.389062874251497)(1837.5,14.099278443113771)(2171.5,18.174152694610775)(2505.5,22.56328143712575)(2839.5,27.240485029940118)(3173.5,32.199152694610774)(3507.5,37.44004491017964)(3841.5,42.9565)(4175.5,48.74484730538922)(4509.5,54.80647305389222)(4843.5,61.164)(5177.5,67.82197005988024)(5511.5,74.77786826347305)(5845.5,82.05068862275449)(6179.5,89.64715269461078)(6513.5,97.57394011976048)(6847.5,105.86460479041916)(7181.5,114.52601796407185)(7515.5,123.56620359281438)(7849.5,133.02156886227544)(8183.5,142.95500898203593)(8517.5,153.42188023952096)(8851.5,164.45122754491018)(9185.5,176.06351796407185)(9519.5,188.34054790419162)(9853.5,201.33261676646708)(10187.5,215.11561676646707)(10521.5,229.66456886227544)(10855.5,244.98857185628742)(11189.5,261.1554341317365)(11523.5,278.16943113772453)(11857.5,296.0684610778443)(12191.5,314.8944161676647)(12525.5,334.76406886227545)(12859.5,355.686380239521)(13193.5,377.6354700598802)(13527.5,400.7926766467066)(13861.5,425.26753293413174)(14195.5,451.1214670658683)(14529.5,478.60874251497006)(14863.5,507.8448353293413)(15197.5,538.9790179640718)(15531.5,572.0008802395209)(15865.5,607.0877035928144)(16199.5,644.1859670658683)(16533.5,683.3988143712575)(16867.5,724.9113922155688)(17201.5,768.7641467065869)(17535.5,815.1436047904191)(17869.5,864.0901227544911)(18203.5,915.7329730538922)(18537.5,970.133739520958)(18871.5,1027.413368263473)(19205.5,1088.0779311377246)(19539.5,1152.6376377245508)(19873.5,1221.4731976047904)(20207.5,1294.8711916167663)(20541.5,1373.1157784431136)(20875.5,1457.0711646706588)(21209.5,1547.5486616766466)(21543.5,1645.0836676646707)(21877.5,1749.5506556886228)(22211.5,1861.3744251497005)(22545.5,1980.2774341317365)(22879.5,2106.45052994012)(23213.5,2240.55351497006)(23547.5,2382.9252964071857)(23881.5,2533.9247964071856)(24215.5,2694.0401377245507)(24549.5,2863.199398203593)(24883.5,3042.0251796407188)(25217.5,3230.280344311377)(25551.5,3428.0554790419164)(25885.5,3636.7262814371256)(26219.5,3857.1243083832333)(26553.5,4090.237161676647)(26887.5,4338.172107784431)(27221.5,4602.643706586827)(27555.5,4887.577766467066)(27889.5,5196.619589820359)(28223.5,5533.495835329341)(28557.5,5904.957110778443)(28891.5,6318.40652994012)(29225.5,6784.988535928144)(29559.5,7319.875413173652)(29893.5,7949.884458083832)(30227.5,8725.226431137724)(30561.5,9789.064071856288)(30895.5,11265.184853293413)(31229.5,13413.724155688624)(31563.5,16944.67256287425)(31897.5,22938.68886227545)(32231.5,32316.48101497006)(32549.5,45359.79038741722)(32702,53261.719)};
\addlegendentry{CVC5}

\addplot[name path=pathOstrichCEA , colourOstrichCEA, line width=1.5pt, solid] coordinates {(1,1.069)(190.5,232.6589)(570.5,709.6480842105263)(950.5,1196.6337184210527)(1330.5,1690.1221210526317)(1710.5,2189.6400842105263)(2090.5,2694.497357894737)(2470.5,3204.0573736842107)(2850.5,3718.6741578947367)(3230.5,4238.482794736841)(3610.5,4764.7214894736835)(3990.5,5298.296757894736)(4370.5,5841.281960526316)(4750.5,6395.202660526315)(5130.5,6961.350839473685)(5510.5,7540.993026315789)(5890.5,8133.372015789473)(6270.5,8734.822897368422)(6650.5,9342.967752631579)(7030.5,9956.752307894736)(7410.5,10575.234568421052)(7790.5,11198.100728947367)(8170.5,11824.840531578946)(8550.5,12455.626292105264)(8930.5,13090.247586842104)(9310.5,13728.575228947368)(9690.5,14370.440260526317)(10070.5,15015.841252631579)(10450.5,15664.630397368423)(10830.5,16317.030813157895)(11210.5,16973.154363157893)(11590.5,17632.737636842106)(11970.5,18295.751634210526)(12350.5,18962.31434736842)(12730.5,19632.349584210526)(13110.5,20305.699439473687)(13490.5,20982.394255263156)(13870.5,21662.506336842103)(14250.5,22345.894881578948)(14630.5,23032.483915789475)(15010.5,23722.286118421052)(15390.5,24415.212605263157)(15770.5,25111.176465789475)(16150.5,25810.02410263158)(16530.5,26511.73647105263)(16910.5,27216.409768421054)(17290.5,27924.022686842105)(17670.5,28634.736831578946)(18050.5,29348.564321052632)(18430.5,30065.47053947368)(18810.5,30785.48525)(19190.5,31508.688036842104)(19570.5,32235.248236842108)(19950.5,32965.0526631579)(20330.5,33698.28517105264)(20710.5,34434.81481052632)(21090.5,35174.532952631576)(21470.5,35917.895857894735)(21850.5,36665.28371052632)(22230.5,37416.66357368421)(22610.5,38172.28100789474)(22990.5,38931.92542368421)(23370.5,39695.625260526314)(23750.5,40463.389355263156)(24130.5,41235.613436842104)(24510.5,42012.476486842104)(24890.5,42793.96287368421)(25270.5,43580.56005526315)(25650.5,44372.39037105263)(26030.5,45169.62203947368)(26410.5,45972.09492631579)(26790.5,46780.44576842106)(27170.5,47595.067805263156)(27550.5,48416.389299999995)(27930.5,49244.825065789475)(28310.5,50080.321313157896)(28690.5,50923.3093368421)(29070.5,51774.13953684211)(29450.5,52633.453644736845)(29830.5,53501.829744736846)(30210.5,54379.64974210526)(30590.5,55267.43845263158)(30970.5,56166.53594210526)(31350.5,57077.05190263158)(31730.5,57999.50882631579)(32110.5,58934.752134210525)(32490.5,59885.838323684206)(32870.5,60853.76433421053)(33250.5,61840.456797368424)(33630.5,62847.4605)(34010.5,63880.007623684214)(34390.5,64943.45741578947)(34770.5,66040.62170789474)(35150.5,67180.7566394737)(35530.5,68371.20348421052)(35910.5,69634.29873421052)(36290.5,71007.77509473685)(36670.5,72553.45386842104)(37050.5,74590.8398131579)(37260.5,77017.990675)(37282,77894.058)};
\addlegendentry{OstrichCEA}

\addplot[name path=pathOstrich , colourOstrich, line width=1.5pt, dashdotted] coordinates {(1,0.973)(183,190.30856164383562)(548,594.3603315068493)(913,1024.961002739726)(1278,1469.2798904109588)(1643,1923.6285232876712)(2008,2386.440526027397)(2373,2857.0123945205482)(2738,3335.2412931506847)(3103,3820.518504109589)(3468,4312.556301369863)(3833,4811.463101369864)(4198,5316.991939726027)(4563,5828.562306849315)(4928,6346.063736986301)(5293,6868.94305479452)(5658,7396.841920547946)(6023,7929.662317808219)(6388,8467.604142465754)(6753,9010.742153424659)(7118,9558.934805479452)(7483,10111.938605479452)(7848,10669.474978082191)(8213,11231.314112328768)(8578,11797.621369863013)(8943,12368.65250410959)(9308,12944.311830136987)(9673,13524.519564383561)(10038,14109.451419178082)(10403,14698.853712328768)(10768,15293.112660273973)(11133,15892.433191780823)(11498,16496.828142465754)(11863,17106.316189041096)(12228,17721.04000547945)(12593,18340.346950684932)(12958,18964.554947945202)(13323,19594.05018082192)(13688,20228.820687671232)(14053,20869.080038356162)(14418,21514.670046575342)(14783,22165.900589041095)(15148,22822.877701369864)(15513,23485.61907123288)(15878,24154.566920547943)(16243,24829.88501369863)(16608,25511.430641095892)(16973,26198.8236630137)(17338,26892.730293150686)(17703,27593.722350684933)(18068,28301.48203561644)(18433,29016.173605479453)(18798,29737.934356164384)(19163,30466.729484931508)(19528,31202.92680821918)(19893,31946.9248630137)(20258,32698.838134246576)(20623,33459.216728767125)(20988,34229.22386849315)(21353,35008.99332054795)(21718,35798.51410410959)(22083,36598.632827397254)(22448,37409.98307945205)(22813,38232.88135342466)(23178,39067.59715616438)(23543,39915.206906849315)(23908,40775.91306849315)(24273,41650.684063013694)(24638,42540.330361643835)(25003,43445.31521643835)(25368,44367.7068)(25733,45309.33676438356)(26098,46271.140583561646)(26463,47254.96390684932)(26828,48263.57510136987)(27193,49300.231649315065)(27558,50368.124427397255)(27923,51470.418468493146)(28288,52611.19690136986)(28653,53795.38869041095)(29018,55029.08482465754)(29383,56320.12154520548)(29748,57678.96482465754)(30113,59114.90866575342)(30478,60647.17013150685)(30843,62287.70946575342)(31208,64046.39155890411)(31573,65948.76017808219)(31938,68015.45561917809)(32303,70268.4742739726)(32668,72725.02970136987)(33033,75449.96638630137)(33398,78510.05700821918)(33763,81999.3380219178)(34128,86050.69222191781)(34493,90831.67789315069)(34858,96740.15275342466)(35223,104550.05547123287)(35588,116337.4376410959)(35779,125163.37964705883)(35789,125692.196)};
\addlegendentry{Ostrich}

\addplot[name path=pathZ3str3 , colourZ3str3, line width=1.5pt, dashed, dash pattern=on 8pt off 2pt] coordinates {(1,0.012)(146,1.978233676975945)(437,6.271)(728,10.63781443298969)(1019,15.179)(1310,19.835)(1601,24.491)(1892,29.147)(2183,33.827536082474225)(2474,38.724)(2765,43.671)(3056,48.636051546391755)(3347,53.813)(3638,59.053546391752576)(3929,64.473)(4220,70.01970103092785)(4511,75.778)(4802,81.598)(5093,87.44253608247422)(5384,93.503)(5675,99.614)(5966,105.74201030927836)(6257,112.081)(6548,118.483)(6839,124.9422268041237)(7130,131.615)(7421,138.308)(7712,145.08378350515463)(8003,152.059)(8294,159.043)(8585,166.03229209621992)(8876,173.212)(9167,180.487)(9458,187.762)(9749,195.08520618556702)(10040,202.625)(10331,210.191)(10622,217.77952577319587)(10913,225.583)(11204,233.44001030927836)(11495,241.445)(11786,249.593)(12077,257.8093848797251)(12368,266.234)(12659,274.69963230240546)(12950,283.382)(13241,292.1369484536083)(13532,301.108)(13823,310.1481237113402)(14114,319.401)(14405,328.73513402061855)(14696,338.284)(14987,347.95956013745706)(15278,357.8412268041237)(15569,367.892)(15860,378.1011271477663)(16151,388.526)(16442,399.09973539518904)(16733,409.8684982817869)(17024,420.836)(17315,431.97982817869416)(17606,443.3423608247423)(17897,454.9270206185567)(18188,466.716)(18479,478.7367113402062)(18770,491.00674570446733)(19061,503.5473642611684)(19352,516.3713711340206)(19643,529.517793814433)(19934,543.0013092783505)(20225,556.8603848797251)(20516,571.1063608247422)(20807,585.7789175257732)(21098,600.9315738831615)(21389,616.5986323024056)(21680,632.778206185567)(21971,649.4465979381444)(22262,666.6643917525772)(22553,684.4916597938144)(22844,702.9503024054983)(23135,722.1009312714777)(23426,742.000879725086)(23717,762.6884123711341)(24008,784.2621340206185)(24299,806.8419381443299)(24590,830.5944329896906)(24881,855.6907972508591)(25172,882.2354776632303)(25463,910.5732749140893)(25754,940.9522302405497)(26045,973.7337250859107)(26336,1009.525501718213)(26627,1049.177388316151)(26918,1094.1484364261169)(27209,1146.7408178694157)(27500,1210.8287972508592)(27791,1295.0530343642613)(28082,1428.52512371134)(28373,1936.0622164948454)(28541,3951.5852444444445)(28565,4945.078)};
\addlegendentry{Z3str3}

\addplot[name path=pathZ3seq , colourZ3seq, line width=1.5pt, dashed, dash pattern=on 1pt off 2pt] coordinates {(1,0.011)(181.5,2.298024861878453)(543.5,7.39196132596685)(905.5,12.846621546961325)(1267.5,18.578)(1629.5,24.44856629834254)(1991.5,30.594629834254146)(2353.5,37.014)(2715.5,43.66661602209945)(3077.5,50.57362154696132)(3439.5,57.753)(3801.5,65.08817403314917)(4163.5,72.6765)(4525.5,80.4550276243094)(4887.5,88.4337955801105)(5249.5,96.6675)(5611.5,105.07338950276242)(5973.5,113.75666574585635)(6335.5,122.7165)(6697.5,131.92012154696133)(7059.5,141.41022651933702)(7421.5,151.196044198895)(7783.5,161.28051104972374)(8145.5,171.66944198895027)(8507.5,182.3868591160221)(8869.5,193.474908839779)(9231.5,204.9389502762431)(9593.5,216.7948950276243)(9955.5,229.06955801104974)(10317.5,241.797091160221)(10679.5,255.0154502762431)(11041.5,268.74189226519337)(11403.5,283.05802486187844)(11765.5,297.9990718232044)(12127.5,313.6326961325967)(12489.5,330.0478287292818)(12851.5,347.36489779005524)(13213.5,365.62986464088397)(13575.5,385.0328149171271)(13937.5,405.66013259668506)(14299.5,427.5818314917127)(14661.5,450.83144475138124)(15023.5,475.5672955801105)(15385.5,502.0523453038674)(15747.5,530.0259751381216)(16109.5,559.3107375690607)(16471.5,589.8519640883978)(16833.5,621.6678066298342)(17195.5,654.8743176795581)(17557.5,689.4013121546961)(17919.5,725.3846961325967)(18281.5,762.8980635359117)(18643.5,801.907591160221)(19005.5,842.5096629834254)(19367.5,884.8020718232044)(19729.5,928.861544198895)(20091.5,974.7612099447514)(20453.5,1022.6342651933702)(20815.5,1072.5725607734807)(21177.5,1124.8395055248618)(21539.5,1179.584991712707)(21901.5,1237.1880303867404)(22263.5,1297.957046961326)(22625.5,1362.265491712707)(22987.5,1430.3952762430938)(23349.5,1502.6981519337016)(23711.5,1579.696502762431)(24073.5,1661.6038812154698)(24435.5,1748.4525828729281)(24797.5,1840.9641022099447)(25159.5,1938.9034005524863)(25521.5,2042.6551602209943)(25883.5,2153.1485220994473)(26245.5,2271.2495)(26607.5,2396.9298314917123)(26969.5,2530.6465359116023)(27331.5,2672.95844198895)(27693.5,2824.6903425414366)(28055.5,2986.2353867403317)(28417.5,3158.2669364640883)(28779.5,3341.9625939226516)(29141.5,3538.530229281768)(29503.5,3748.9704861878454)(29865.5,3973.6326353591157)(30227.5,4215.252831491713)(30589.5,4476.184969613259)(30951.5,4760.791403314917)(31313.5,5071.179861878453)(31675.5,5412.076848066298)(32037.5,5786.981693370165)(32399.5,6205.653919889503)(32761.5,6683.778737569061)(33123.5,7242.432157458564)(33485.5,7909.979223756905)(33847.5,8733.536740331492)(34209.5,9802.194723756906)(34571.5,11351.004914364641)(34933.5,13998.519212707182)(35279.5,19650.679766666664)(35446,25499.5)};
\addlegendentry{Z3seq}
